Are Modern Byte Pair Tokenizers Zipfian?

### 2025-05-12 writeup/paper.tex
title and authors

% Change "review" to "final" to generate the final (sometimes called camera-ready) version.
% Change to "preprint" to generate a non-anonymous version with page numbers.
\usepackage[review]{acl}

@@

\title{Instructions for *ACL Proceedings}

@@

\author{First Author \\
  Affiliation / Address line 1 \\
  Affiliation / Address line 2 \\
  Affiliation / Address line 3 \\
  \texttt{email@domain} \\\And
  Second Author \\
  Affiliation / Address line 1 \\
  Affiliation / Address line 2 \\
  Affiliation / Address line 3 \\
  \texttt{email@domain} \\}

>>>>

% Change "review" to "final" to generate the final (sometimes called camera-ready) version.
% Change to "preprint" to generate a non-anonymous version with page numbers.
% \usepackage[review]{acl}
\usepackage[preprint]{acl}

@@

\title{Are Modern Byte Pair Tokenizers Zipfian?}

@@

\author{Jack Hanke \\
  Northwestern University \\
  \And
  Daniel Plotkin \\
  Northwestern University \\
  \And
  Nicole Birova \\
  Northwestern University}
